Explore CNV distributions of reference cells: SCPCP000015

### 2025-06-02 analyses/infercnv-consensus-cell-type/exploratory-notebooks/02_ewings-reference-cnv.Rmd
fixed a couple formatting spots

```{r}
plot_cnv_distributions <- function(df, reference_name) {
  filtered_df <- infercnv_df |>
    dplyr::filter(normal_reference == reference_name)

@@

```{r, fig.width = 10, fig.height = 8, message = FALSE}
plot_cnv_distributions(infercnv_df, "endo_pooled")
plot_cnv_distributions(infercnv_df, "immune_pooled")
plot_cnv_distributions(infercnv_df, "endo-immune_pooled")
```

>>>>

```{r}
plot_cnv_distributions <- function(reference_name, df) {
  filtered_df <- df |>
    dplyr::filter(normal_reference == reference_name)

@@

```{r, fig.width = 10, fig.height = 8, message = FALSE}
unique(infercnv_df$normal_reference) |>
  purrr::map(plot_cnv_distributions, infercnv_df)
```
